HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-21 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Proper citations for Training Paper (#94)
Add citations to be used in Training and Careers paper to CWP bib file
Fix many typos and minor errors in main paper

It is also critical to incorporate training into grant proposals so that it can
be connected with other areas such as research and development. Efforts like
DIANA-HEP~\cite{DIANA-HEP} and aMVA4NewPhysics~\cite{aMVA4NewPhysics}
that combine training
and software development are good examples of such ideas in practice. More
examples of such efforts are needed.

>>>>

It is also critical to incorporate training into grant proposals so that it can
be connected with other areas such as research and development. Efforts like
DIANA-HEP~\cite{DIANA-HEP} and AMVA4NewPhysics~\cite{AMVA4NewPhysics}
that combine training
and software development are good examples of such ideas in practice. More
examples of such efforts are needed.
